\section{External Interface Requirements}

\subsection{User Interfaces}

Defines the look and feel of the system's interfaces, ensuring usability and accessibility for all user classes.

Requirements:

The system shall provide a responsive design compatible with various screen sizes.

The system shall use intuitive navigation menus for ease of use.

The system shall display notifications and alerts for important actions and errors.

The system shall support multiple languages as per user preferences.

Wireframes:

Login Page: Simple and secure login interface.

Dashboard: Overview of recent activities and quick access to features.

Scan Interface: Camera view with scanning indicators.

Document View: Detailed view of scanned documents with verification status.

\subsection{Hardware Interfaces}

Description: It specifies the hardware components that the system will interact with.

Requirements:

The system shall interface with device camera and mic for interactive live classes.

The system shall support external device connections.

The system shall be compatible with standard mobile device sensors for optimal scanning performance.

The system should support decent level internet speed.

\subsection{Software Interfaces}

The system shall integrate with existing device’s browser through web application.

The system shall use third-party libraries for faster results.

The system shall interface with authentication services.

The system shall support data synchronization with cloud storage solutions.

\subsection{Communications Interfaces}

The system shall use HTTPS for all data transmissions to ensure proper security.

The system shall enable real-time data updates using capable technologies.

The system shall provide notifications through email or other communicable sites.
