\section{Introduction}

\subsection{Purpose}

The SRS documentation will provide a detailed understanding about “11th Lesson” which is an e-learning web-based platform. The platform is designed to provide high end materials like hand notes and interactive videos for both teachers and students which is specially academic oriented and will help to prepare for the exam at last hour in a more efficient and organized way. The document outlines the system’s functionality and features to maintain a good interaction between the stakeholders and the developers which will give a better outcome to fulfill the project’s objectives.

\subsection{Document Conventions}

Top Left Corner: Indicates the page content.\\
Top Right Corner: Indicates the page serial.\\
Bold Text: Indicates section titles and important keywords.\\
Numbering: Follows a hierarchical structure (e.g., 1.1, 1.2).\\
Bullet Points: Used for listing items and features.

\subsection{Intended Audience and Reading Suggestions}

Developers: For understanding system functionalities and further improving requirements.\\
Project Managers: Ensuring the project requirements to be fulfilled.\\
Quality Assurance: Designing and executing among the test cases based on all the possible requirements.\\
Stakeholders: Verifying the system as promised and ensuring it meets all needs and expectations.

\subsection{Project Scope}

"11th Lesson" aims to organize all the necessary study materials like audio, video and pdfs a student needs to prepare for exam in the last moment and same goes for the teachers. The system will provide interactive tutorials based on the academic courses reducing the need for manually organizing materials before exam and minimizing the time of preparation. Key functionalities include Live and Downloaded classes across the web for free, having personal Id and Dashboards, Upload and Download Notes and Videos like open source, and Ratings based on the materials quality.

\subsection{References}

Stack Overflow: A Q\&A platform where developers share knowledge and solve coding problems.\\
GeekforGeeks: A go-to resource for learning algorithms, data structures and other programming languages.\\
W3Schools: It offers tutorials and references on development topics.\\
10 minutes School: Provides short, engaging lessons on academic courses in a simplified manner.
