\section{Other Nonfunctional Requirements}

\subsection{Performance Requirements}

The system shall process and display the desired window in as minimal latency as possible.

The system shall support up to 10,000 concurrent users without performance degradation.

The system shall have an uptime of 99.9%, excluding scheduled maintenance.

The system shall handle peak loads during high-traffic periods, such as exam times.

\subsection{Safety Requirements}

The system shall not interfere with the existent account of any other users or guest accounts.

The system shall ensure that sensitive data is not exposed to unauthorized individuals during use.

The system shall include safeguards to prevent accidental data loss.

\subsection{Security Requirements}

The system shall encrypt all sensitive data both in transit and at rest using industry-standard encryption algorithms.

The system shall implement role-based access control to restrict data access based on user roles.

The system shall log all access attempts and modifications for auditing purposes.

The system shall regularly update and patch all software components to mitigate vulnerabilities.

The system shall perform regular security assessments and penetration testing.

\subsection{Software Quality Attributes}

Reliability: The system shall maintain consistent performance without failures.

Maintainability: The system's codebase shall be modular and well-documented to facilitate maintenance and updates.

Usability: The system shall provide an intuitive and user-friendly interface to enhance user experience.

Scalability: The system shall be designed to accommodate future growth in user base and data volume.

Portability: The system shall be deployable across various platforms and devices with minimal modifications.
